Speeding up decimal multiplication

### 2020-11-22 paper/paper.tex
Update

The code of our implementation, benchmark scripts, and \LaTeX source of this paper,
are available at \url{https://github.com/shdown/decimal-multiplication-paper}.
The code is licensed under the MIT license.
The source of this paper is licensed under the Creative Commons BY 4.0 license.

>>>>

The code of our implementation, benchmark scripts, and \LaTeX{}
source of this paper,
are available at \url{https://github.com/shdown/decimal-multiplication-paper}.
The code is licensed under the MIT license.
The source of this paper is licensed under the Creative Commons BY 4.0 license.
